---
title: "Final_submission_homework_2_of_Yue_Ma"
author: "Yue Ma"
date: "2018/9/26"
always_allow_html: yes
output: 
   html_document:
     keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Selection of Data and Tidying 

```{r echo=FALSE}
setwd("/Users/mayue/Documents/GitHub/Ma_Yue/hw02")
library(readxl)
library(reprex)
library(tidyverse)
library(tidyr)
raw_data <- read.csv("U.S._Chronic_Disease_Indicators__CDI_.csv")
clean_data_1 <- raw_data %>%
  filter(Question == "Binge drinking prevalence among adults aged >= 18 years") %>%
  filter(DataValueType == "Crude Prevalence") %>%
  filter(Stratification1 == "Overall"|Stratification1 == "Male"|Stratification1 == "Female")
selected_data_1 <- clean_data_1 %>%
  select(state = LocationDesc, year = YearStart, DataValue, Stratification1)
head(selected_data_1)
selected_data_1 <- spread(selected_data_1, key = Stratification1, value = DataValue)
selected_data_1 <- unite_(selected_data_1, "state_year", c("state","year"))
```

```{r echo=FALSE}
clean_data_2 <- raw_data %>%
  filter(Question == "Poverty") %>%
  filter(DataValueType == "Crude Prevalence") %>%
  filter(Stratification1 == "Overall")
selected_data_2 <- clean_data_2 %>%
  select(state = LocationDesc, stateabb = LocationAbbr, year = YearStart, DataValue, Stratification1)
head(selected_data_2)
selected_data_2 <- spread(selected_data_2, key = Stratification1, value = DataValue)
selected_data_2 <- unite_(selected_data_2, "state_year", c("state","year"))
```

## Cleaned dataset in a tidy state-year format

```{r echo=FALSE}
binge_clean <- full_join(selected_data_2, selected_data_1, by = "state_year")
head(binge_clean)
binge_clean <- binge_clean %>%
  separate("state_year", into = c("state","year"), sep="_") %>%
select(state, stateabb, year, binge_all = Overall.y, binge_male = Male, binge_female = Female, poverty = Overall.x)
binge_clean$binge_all = as.numeric(as.character(binge_clean$binge_all))
binge_clean$binge_male = as.numeric(as.character(binge_clean$binge_male))
binge_clean$binge_female = as.numeric(as.character(binge_clean$binge_female))
binge_clean$poverty = as.numeric(as.character(binge_clean$poverty))
print(binge_clean)
setwd("/Users/mayue/Documents/GitHub/Ma_Yue/hw02")
write_csv(binge_clean, "binge_clean.csv")
```

# Data Transformation and Summary Results

## Top 10 binge drinking states  

```{r echo=FALSE}
binge_top_10 <- binge_clean %>%
  select(state, stateabb, year, binge_all, binge_male, binge_female) %>%
  filter(year == "2016") %>%
  arrange(desc(binge_all)) %>%
  head(n=10)
print(binge_top_10)
```

## Scatter plot

From the scatter plot below: I find that there is an obvious negative correlation between the the poverty prevalence and the overall binge drinking prevalence in a state.

```{r echo=FALSE}
library(ggplot2)
p <- ggplot(binge_clean, aes(poverty, binge_all))
q <- p + geom_point() + ggtitle('Correlation between the poverty prevalence and the overall binge drinking prevalence')+ ylab("Overall binge drinking prevalence") + xlab("Overall poverty prevalence") + geom_smooth()
print(q)
```


## Annual growth rate

The first is the table of the 5 states with the largest increases and the second is the table of the 5 states with the largest decreases in binge drinking prevalence over the time period. 

```{r echo=FALSE}
library(dplyr)
growth_rate1 <- binge_clean %>%
  group_by(state) %>%
  summarise(annualgrowth = (first(na.omit(binge_all)) - last(binge_all))/n()) %>%
  select(state, annualgrowth) %>%
  arrange(desc(annualgrowth)) %>% 
  top_n(5)
print(growth_rate1, digits = 2)
```

```{r echo=FALSE}
library(dplyr)
growth_rate2 <- binge_clean %>%
  group_by(state) %>%
  summarise(annualgrowth = (first(na.omit(binge_all)) - last(binge_all))/n()) %>%
  select(state, annualgrowth) %>%
  arrange(annualgrowth) %>%
  head(5)
print(growth_rate2, digits = 2)
```


