---
title: "Final submission homework 3 of Yue Ma"
author: "Yue Ma"
date: "2018/10/3"
always_allow_html: yes
output: 
   html_document:
     keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1. Beer Song

## a) Write a loop

(Note: from 99 to 0 bottle)

```{r eval = FALSE, echo=TRUE}
x <- 99
  for (i in c(rev(seq_len(x)), 0)) {
    if (i == 0) {
      cat(glue::glue("No more bottles of beer on the wall, no more bottles of beer.\n Go to the store and buy some more, {x} bottles of beer on the wall."))
    } else {
      cat(glue::glue("{i} {if (i == 1) 'bottle' else 'bottles'} of beer on the wall, {i} {if (i == 1) 'bottle' else 'bottles'} of beer.\n Take one down and pass it around, {if (i == 1) 'no more' else i - 1} bottles of beer on the wall. \n \n \n"))
    }
  }
```

(Note: from 99 to 95 bottles)

```{r echo=TRUE}
x <- 99
  for (i in c(seq(from = x, to = x - 4), 0)) {
    if (i == 0) {
      cat(glue::glue("No more bottles of beer on the wall, no more bottles of beer.\n Go to the store and buy some more, {x} bottles of beer on the wall."))
    } else {
      cat(glue::glue("{i} {if (i == 1) 'bottle' else 'bottles'} of beer on the wall, {i} {if (i == 1) 'bottle' else 'bottles'} of beer.\n Take one down and pass it around, {if (i == 1) 'no more' else i - 1} bottles of beer on the wall. \n \n \n"))
    }
}
```

## b) Convert loop to a function

```{r echo=TRUE}
beersong <- function(x, liquid) {
  
  for (i in c(rev(seq_len(x)), 0)) {
    if (i == 0) {
      cat(glue::glue("No more bottles of {liquid} on the wall, no more bottles of wall.\n Go to the store and buy some more, {x} bottles of {liquid} on the wall."))
    } else {
      cat(glue::glue("{i} {if (i == 1) 'bottle' else 'bottles'} of {liquid} on the wall, {i} {if (i == 1) 'bottle' else 'bottles'} of {liquid}.\n Take one down and pass it around, {if (i == 1) 'no more' else i - 1} bottles of {liquid} on the wall. \n \n \n"))
    }
  }
}
beersong(3, 'Whiskey')
```

## c) Add error check

```{r echo=TRUE}
beersong <- function(x, liquid) {
  
 if (is.numeric(x)) {
  for (i in c(rev(seq_len(x)), 0)) {
     if (i == 0) {
      cat(glue::glue("No more bottles of {liquid} on the wall, no more bottles of wall.\n Go to the store and buy some more, {x} bottles of {liquid} on the wall."))
    } else {
      cat(glue::glue("{i} {if (i == 1) 'bottle' else 'bottles'} of {liquid} on the wall, {i} {if (i == 1) 'bottle' else 'bottles'} of {liquid}.\n Take one down and pass it around, {if (i == 1) 'no more' else i - 1} bottles of {liquid} on the wall. \n \n \n"))
    }
   } 
  } else {
    cat("Ooooops...Error! Please enter a number.")
  }  
}  

beersong("beer", "Pepsi")
```

```{r echo=TRUE}
beersong <- function(x, liquid) {
  
 if (is.numeric(x)) {
  for (i in c(rev(seq_len(x)), 0)) {
     if (i == 0) {
      cat(glue::glue("No more bottles of {liquid} on the wall, no more bottles of wall.\n Go to the store and buy some more, {x} bottles of {liquid} on the wall."))
    } else {
      cat(glue::glue("{i} {if (i == 1) 'bottle' else 'bottles'} of {liquid} on the wall, {i} {if (i == 1) 'bottle' else 'bottles'} of {liquid}.\n Take one down and pass it around, {if (i == 1) 'no more' else i - 1} bottles of {liquid} on the wall. \n \n \n"))
    }
   } 
  } else {
    cat("Ooooops...Error! Please enter a number.")
  }  
}  

beersong(3, "Pepsi")
```

## d) Convert loop to a fully generalized function

```{r echo=TRUE}
beersong <- function(x, vessel, liquid, place) {
  
 if(is.numeric(x)) {
  for (i in c(rev(seq_len(x)), 0)) {
     if (i == 0) {
      cat(glue::glue("No more {vessel} of {liquid} on the {place}, no more {vessel} of {place}.\n Go to the store and buy some more, {x} {vessel}s of {liquid} on the {place}."))
    } else {
      cat(glue::glue("{i} {if (i == 1) {vessel} else {vessel}} of {liquid} on the {place}, {i} {if (i == 1) {vessel} else {vessel}} of {liquid}.\n Take one down and pass it around, {if (i == 1) 'no more' else i - 1} {vessel} of {liquid} on the {place}. \n \n \n"))
    }
   } 
  } else {
    cat("Ooooops...Error! Please enter a number.")
  }  
}  

beersong(3, "jugs", "milk", "shelf")
```

# 2. Draw a plot using a loop

## a) Plot with horizontal lines

```{r echo=TRUE}
plot(1, type = "n", xlab = "", ylab = "", xlim = c(0, 10), ylim = c(0, 10))
m <- 10
for (i in c(seq_len(m), 0)) {
  lines(x = c(0, 10), y = c(i, i))
}
```

## b) Add vertical lines

```{r echo=TRUE}
plot(1, type = "n", xlab = "", ylab = "", xlim = c(0, 10), ylim = c(0, 10))
m <- 10
n <- 10
for (i in c(seq_len(m), 0)) {
  lines(x = c(0, 10), y = c(i, i))
}
for (t in c(seq_len(n), 0)) {
  lines(x = c(t, t), y = c(0, 10))
}
```

## c) Add points

```{r echo=TRUE}
plot(1, type = "n", xlab = "", ylab = "", xlim = c(0, 10), ylim = c(0, 10))
m <- 10
n <- 10
for (i in c(seq_len(m), 0)) {
  lines(x = c(0, 10), y = c(i, i))
  points(x = i, y = i)
  points(x = i, y = 10 - i)
}
for (t in c(seq_len(n), 0)) {
  lines(x = c(t, t), y = c(0, 10))
}
```

## d) Convert to function

Note: the user to set the size of the plot (the plot should be square) and which items to draw (Hline - horizontal lines, Vline - vertical lines, point_diagonal - points on the diagonal). 

Enter number to set the size of the plot.
Enter "Y" or "N" to choose if you want to draw the item.

```{r eval = FALSE, echo=TRUE}

draw_function <- function(size = 10, Hline = FALSE, Vline = FALSE, point_diagonal = TRUE) {

plot(1, type = "n", xlab = "", ylab = "", xlim = c(0, {size}), ylim = c(0, {size}))
if ({Hline} == "Y" && {Vline} == "Y" && {point_diagonal} == "Y") {
for (i in c(seq_len({size}), 0)) {
  lines(x = c(0, {size}), y = c(i, i))
  lines(x = c(i, i), y = c(0, {size}))
   points(x = i, y = i)
  points(x = i, y = {size} - i)
} 
} else if ({Hline} == "N" && {Vline} == "Y" && {point_diagonal} == "Y") {
 for (i in c(seq_len({size}), 0)) {
   lines(x = c(i, i), y = c(0, {size}))
   points(x = i, y = i)
  points(x = i, y = {size} - i)
}
} else if ({Hline} == "Y" && {Vline} == "N" && {point_diagonal} == "Y") {
  for (i in c(seq_len({size}), 0)) {
   lines(x = c(0, {size}), y = c(i, i))
   points(x = i, y = i)
  points(x = i, y = {size} - i)
  }
} else if ({Hline} == "Y" && {Vline} == "Y" && {point_diagonal} == "N") {
  for (i in c(seq_len({size}), 0)) {
  lines(x = c(0, {size}), y = c(i, i))
  lines(x = c(i, i), y = c(0, {size}))
  }
} else if ({Hline} == "Y" && {Vline} == "N" && {point_diagonal} == "N") {
  for (i in c(seq_len({size}), 0)) {
   lines(x = c(0, {size}), y = c(i, i))
  }
} else if ({Hline} == "N" && {Vline} == "Y" && {point_diagonal} == "N") {
 for (i in c(seq_len({size}), 0)) {
   lines(x = c(i, i), y = c(0, {size}))
 }
} else if ({Hline} == "N" && {Vline} == "N" && {point_diagonal} == "Y") {
 for (i in c(seq_len({size}), 0)) {
   points(x = i, y = i)
  points(x = i, y = {size} - i)
 }
} else if ({Hline} == "N" && {Vline} == "N" && {point_diagonal} == "N") {

}
}  

draw_function(10, "Y", "N", "Y")
draw_function(8, "Y", "Y", "Y")
  
```


