---
title: "Final Submission Homework 8 of Yue Ma"
author: "Yue Ma"
date: "11/15/2018"
always_allow_html: yes
output: 
   html_document:
     keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Writing a simple API client

## 1. Choose an API

a) I choose Yelp Business search API, I can get the data about businesses by keyword, category, location, price level, etc using this API.

b) The link to the API documentation is : https://www.yelp.com/developers/documentation/v3/business_search

c) The base URL of Yelp business search API I intend to use is : https://api.yelp.com/v3/businesses/search

## 2. Authentication

a) Briefly explain how the API authenticates the user:
Yelp Fusion API uses private API Keys to authenticate requests. To authenticate the call to an endpoint, there are only 2 steps: The first step is to create an app to obtain your private API Key. The second step is to authenticate API calls with the API Key.

b) To get my API key, I firstly create APP in the url: https://www.yelp.com/developers/v3/manage_app. After getting my API key, I save your account key in the .Renviron file:
## Yelp Fusion API Key
Yelp_Fusion_Key = b83YP7YDDX...
Then, I authenticated API calls with the API Key by setting the Authorization HTTP header value as Bearer API_KEY.(details see below in 3 part)
The relevant URL is: https://www.yelp.com/developers/documentation/v3/authentication

## 3. Send a Simple GET request
```{r echo=TRUE}
library(httr)
library(purrr)
API_key <- Sys.getenv("Yelp_Fusion_Key")
baseurl_yelp <- "https://api.yelp.com/v3/businesses/search"
term <- "restaurants"
location <- "New York City"
limit <- 50
radius <- 16094
r <- GET(baseurl_yelp,
         query = list(term = term, location = location, 
                               limit = limit,
                               radius = radius),
         add_headers('Authorization' = paste("Bearer", API_key)))
http_status(r)
http_type(r)
```

I choose 4 query parameters here: term, location, limit and radius.
I want to find all Dunkin Donuts locations within 10 miles (16094 meters) of New York City:
The term is business name with "restaurants".
The location indicates the geographic area to be used when searching for businesse with "New York City".
The limit indicates the number of business results to return with "50".
The radius is used as a suggestion to the search within 10 miles (16094 meters).

As the results above, the status of the request is 200 (success), the type of the response is JSON.

## 4. Parse the response and Create a dataset
a) Take the response returned by the API and turn it into a data frame. Show the code how this is done.
```{r echo=TRUE}
r
```

The results above show the response returned by the API.

```{r echo=TRUE}
library(jsonlite)
cont <- r$content
char <- rawToChar(r$content)
df <- fromJSON(char, simplifyDataFrame = TRUE)
typeof(df)
names(df)
names(df$businesses)
```
I turn it into a usefsul R object - list, seen as above, including business, total and region.
The business is a dataframe showing some usesful information, including id, alias, name, review account, rating, phone number, price, and distance. 

b) Create a dataset (in data frame format) for multiple records.
```{r echo=FALSE}
library(dplyr)
NYC_restaurants <- df$businesses %>%
  select(id, name, rating, review_count, location, price, phone, distance)
head(NYC_restaurants)
```
I create the dataset called NYC_restaurant, which indicates some usesful information of restaurants within 10 miles of New York City (the region center is (-73.99429, 40.70544)). The dataframe above shows 6 rows of the dataset. Due to the API limit with maximum of 50, I can just create a dataset with size of 50 maximum. The full size dataset is the file called __data.rds__.

c) Provide some summary statistics of the data.
```{r echo=FALSE}
NYC_restaurants1 <- NYC_restaurants %>%
  select(-location)
summary(NYC_restaurants1)
table(NYC_restaurants1$price)
NYC_restaurants2 <- NYC_restaurants1 %>%
  filter(price == "$$$") %>%
  select(name)
NYC_restaurants2
saveRDS(NYC_restaurants, file = "data.rds")
```
From the results above, we can get the conclusion below: (analysis based on 50 restaurants showed within 10 miles of NYC)
1. The mean of the restaurant rating is 4.22 out of 5.00, which indicates that the quality of the targeted restaurants is high.
2. The mean of the review counts of the restaurant is 1121.6, the restaurant with the most review counts is Joe's Shanghai with 5480 reviews; the restaurant with the least review counts is Bernie's with 16 reviews.
3. The mean of the distance of the restaurant is 3168.7 meters.
4. 47 out of 50 restaurants have a price level of 2 dollars, and 2 out of 50 restaurants have a price level of 3 dollars, which indicates that most of the restaurants have a modest price. The 2 restuarants with higher price level are Boucherie West Village, and Antica Ristorante.

## 5. API Client
```{r echo=TRUE}
yelp_business_search <- function(term = "food", location = "New York City", 
                                 radius = "16094", limit = "10", return_type = "dataframe") {
  
  baseurl_yelp <- "https://api.yelp.com/v3/businesses/search"
  r <- GET(baseurl_yelp,
         query = list(term = term, location = location, 
                               limit = limit,
                               radius = radius),
         add_headers('Authorization' = paste("Bearer", API_key)))
  if (http_error(r)){
    warning("The request produced an error.")
  } else {
    r
    cont <- r$content
    char <- rawToChar(r$content)
    df <- fromJSON(char, simplifyDataFrame = TRUE)
  if (return_type == "dataframe"){
    finalresults <- df$businesses %>%
      select(id, name, rating, review_count, location, price, phone, distance)
    print(finalresults) 
  } else{
    df
  }
  }
}

NYC_food <- yelp_business_search(term = "food", location = "New York City", radius = "16094", limit = "10", return_type = "dataframe")
saveRDS(NYC_food, file = "api_client_output.RDS")
```

The above returns for the default values.

```{r echo=TRUE}
yelp_business_search(term = "sports", location = "PA", radius = "16094", limit = "5", return_type = "list")
```

The above returns the values with list.

```{r}
yelp_business_search(term = "sports", location = "PA", radius = "160940", limit = "5", return_type = "list")
```

The above informs the user of any errors.

