---
title: "Final submission homework 7 of Yue Ma"
author: "Yue Ma"
date: "11/5/2018"
always_allow_html: yes
output: 
   html_document:
     keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Calling an API using httr

## 1. Define the base URL

```{r echo=FALSE}
library(httr)
library(purrr)
R.home(component = "home")
endpoint <- "https://data.lacity.org/resource/7fvc-faax.csv"
endpoint
```

## 2. Send a simple GET request
```{r echo=FALSE}
LA_crime <- GET(endpoint)
str(LA_crime, max.level = 1)
```

From the information above, we can see that the status code starts with 2, so it is great.
The structure of the response is as above as well.

## 3. Get the content of the response
```{r echo=FALSE}
content_LA_crime <- content(LA_crime)
dim(content_LA_crime)
table(content_LA_crime$area_name)
```

There are 1000 observations of 36 variables in the data frame. The table shows the areas of the observations included.

## 4. Get your access token
```{r echo=FALSE}
query_params <- list(
  "$$app_token" = Sys.getenv("LACRIME_APP_TOKEN"),
  "$limit" = "10000")
    
parameter_response <-
  GET("https://data.lacity.org", 
      query = query_params)

parameter_response$status_code
```
From the result above, after resending the query with the fields: "limit" = "10000" and "app_token" = Sys.getenv("LACRIME_APP_TOKEN") as query parameterswe, we can see that the status of the server response with 200 is great.

## 5. Limiting your query
```{r echo=FALSE}
query_params1 <- list(
  "$$app_token" = Sys.getenv("LACRIME_APP_TOKEN"),
  "$limit" = "10000",
  "area_id" = "01",
  "vict_sex" = "M")
    
parameter_response1 <-
  GET("https://data.lacity.org", 
      query = query_params1)

parameter_response1$status_code
```

I added two more query field parameters - area id and victim sex. I select area id = 01, which selects Central area. I aslo select victim sex = M, which selects male victims.
The status of the server response is 200, so it is still great.

## 6. Locations
```{r echo=FALSE}
library(plyr)
library(dplyr)
library(tidyr)
LA_crime_location <- content_LA_crime %>%
  select(location_1) %>%
  head(50) %>%
  separate(location_1, c("point", "longitude1", "latitude"), sep = " ")%>%
  select(latitude, longitude1) %>%
  separate(latitude, c("latitude", "none")) %>%
  unite(latitude, latitude, none, sep = ".") %>%
  separate(longitude1, c("none1", "longitude1"), sep = "-") %>%
  select(latitude, longitude1)
LA_crime_location$longitude1 = as.numeric(as.character(LA_crime_location$longitude1))
LA_crime_location$latitude = as.numeric(as.character(LA_crime_location$latitude))
LA_crime_location <- LA_crime_location %>%
  mutate(longitude = longitude1 * (-1)) %>%
  select(latitude, longitude) %>%
  unite(latlng, latitude, longitude, sep = ",")


for (i in 1:50) {
  url <- paste("https://maps.googleapis.com/maps/api/geocode/json?", "latlng=", LA_crime_location[i,1], "&key=", Sys.getenv("GOOGLE_MAP_KEY"), sep = "")
  result <- GET(url)
  Sys.sleep = 0.1
  if(http_error(result)){
	warning("The request produced an error.")
} else {
  print(content(result)$results[[1]]$formatted_address)
}}

```
From the results above, we can see the addresses for 50 entries in my dataset based on their latitude and longitude. 
