---
title: "Final Submission Homework 9 of Yue Ma"
author: "Yue Ma"
date: "11/21/2018"
always_allow_html: yes
output: 
   html_document:
     keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Web Scraping with Selectors

## 1. Get HTML
```{r}
library(xml2)
library(httr)
library(rvest)
url_wiki <- "https://en.wikipedia.org/wiki/Mitch_McConnell"
wiki <- read_html(url_wiki)
wiki
mm_table <- html_node(x = wiki, xpath = '//*[@id="mw-content-text"]/div/table[2]')
mm_table
```

## 2. Get the info box
a) Find the CSS class of the infobox.
THe CSS class of the infobox is "infobox.vcard".

b) Extract the part of the HTML document that contains the infobox using the CSS information.
```{r}
infobox <- wiki %>%
  html_node(".infobox.vcard") %>%
  html_table() 
infobox
```

## 3. Make a data frame
a) Parse the infobox table HTML you obtained above into a data frame.
```{r}
infobox_dataframe <- as.data.frame(infobox)
head(infobox_dataframe)
```

b) Name the columns of the table you obtain key and value. 
```{r}
library(dplyr)
colnames(infobox_dataframe) <- c("key", "value")
head(infobox_dataframe)
```

c) Filter the data frame.
```{r}
library(stringr)
infobox_dataframe1 <- infobox_dataframe %>%
  filter(key == "Political party" | key == "Children") 
data1 <- data.frame(key = c("Full name"), value = colnames(infobox)) %>%
  head(1)
infobox_dataframe1 <- rbind(data1, infobox_dataframe1)
infobox_dataframe1
```

## 4. Make a function

```{r}
get_wiki_info <- function(url) {
  url_wiki <- url
  wiki <- read_html(url_wiki)
  infobox <- wiki %>%
  html_node(".infobox.vcard") %>%
  html_table() 
  infobox_dataframe <- as.data.frame(infobox)
  colnames(infobox_dataframe) <- c("key", "value")
  infobox_dataframe1 <- infobox_dataframe %>%
  filter(key == "Political party" | key == "Children") 
  data1 <- data.frame(key = c("Full name"), value = colnames(infobox)) %>%
  head(1)
  infobox_dataframe1 <- rbind(data1, infobox_dataframe1)
  infobox_dataframe1
}  

get_wiki_info("https://en.wikipedia.org/wiki/Tammy_Duckworth")
get_wiki_info("https://en.wikipedia.org/wiki/Susan_Collins")
```

Fix the function.
```{r}
get_wiki_info <- function(url) {
  url_wiki <- url
  wiki <- read_html(url_wiki)
  infobox <- wiki %>%
  html_node(".infobox.vcard") %>%
  html_table() 
  infobox_dataframe <- as.data.frame(infobox)
  colnames(infobox_dataframe) <- c("key", "value")
  infobox_dataframe1 <- infobox_dataframe %>%
  filter(key == "Political party" | key == "Children") 
  data1 <- data.frame(key = c("Full name"), value = colnames(infobox)) %>%
  head(1)
  infobox_dataframe1 <- rbind(data1, infobox_dataframe1)
  if (nrow(infobox_dataframe1) == 2) {
    data2 <- data.frame(key = c("Children"), value = c("NA"))
    infobox_dataframe1 <- rbind(infobox_dataframe1, data2)
    infobox_dataframe1
  } else {
  infobox_dataframe1    
  }
}  

get_wiki_info("https://en.wikipedia.org/wiki/Tammy_Duckworth")
get_wiki_info("https://en.wikipedia.org/wiki/Susan_Collins")
```

## 5. Get all senators' pages
a) Get the URLs.
```{r}
url_senator <- "https://en.wikipedia.org/wiki/Current_members_of_the_United_States_Senate"
html_senator <- read_html(url_senator) 
senator <- html_nodes(html_senator, ".fn a") %>%
  xml_attr("href")
link_senator <- paste("https://en.wikipedia.org",senator, sep = "")
link_senator <- as.data.frame(link_senator)
link_senator$senator <- as.character(link_senator$link_senator) 
link_senator <- link_senator %>%
  select(senator)
```

b) Create a loop that uses get_wiki_info function.
```{r}
results <- vector("list", 100)
for (i in 1:100) {
results[[i]] <- get_wiki_info(link_senator[i,])
}
```

c) Clean up your data to provide some summary statistics. How many children does the average senator have? What about by party affiliation?
```{r}
library(tidyr)
total_results <- as.data.frame(results)
total_results <- as.data.frame(t(total_results))
results_dup <- total_results[!duplicated(total_results),]
results_dup <- results_dup[-1,] 
colnames(results_dup) <- c("Full name", "Political party", "Children")
rownames(results_dup) <- NULL
results_dup[9,3] <- 1
results_dup[30,3] <- 3
results_dup[36,3] <- 1
results_dup[43,3] <- 2
results_dup[50,3] <- 4
results_dup[59,3] <- 2
results_dup[61,3] <- 1
results_dup[90,3] <- 1
results_dup[95,3] <- 3
results_dup$Children <- as.numeric(as.character(results_dup$Children))
mean(results_dup$Children, na.rm = TRUE)
```
The senators have 2.75 children on average.


```{r}
democratic_senator <- filter(results_dup, grepl('Democratic', `Political party`)) 
nrow(democratic_senator)
mean(democratic_senator$Children, na.rm = TRUE)
```
There are 47 senators from Democratic party and have 2.45 children on average.

```{r}
republican_senator <- filter(results_dup, grepl('Republican', `Political party`)) 
nrow(republican_senator)
mean(republican_senator$Children, na.rm = TRUE)
```

There are 51 senators from Republican party and have 2.98 children on average.
