---
title: "Final Submission Homework 10 of Yue Ma"
author: "Yue Ma"
date: "12/01/2018"
always_allow_html: yes
output: 
   html_document:
     keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# 1. Getting to know the data

```{r echo=FALSE}
library(DBI)
witch_con <- dbConnect(RMySQL::MySQL(),
                 user='student', 
                 password='mds-is-fun',
                 dbname='witchcraft', 
                 host='tbrambor.cczjcoy6i2jn.us-east-1.rds.amazonaws.com',
                 port = 3306)
```

a) Show a list of the tables.
```{sql echo=TRUE, connection="witch_con"}
-- Check which tables are in the database
SHOW TABLES
```

There are 37 tables included in the database.

b) Display the column names.
```{sql echo=TRUE, connection="witch_con"}
SELECT COLUMN_NAME
FROM INFORMATION_SCHEMA.COLUMNS
WHERE TABLE_NAME = 'accused'
```

There are 32 column names for the table accused.

c) How many people are included in the accused table?
```{sql echo=TRUE, connection="witch_con"}
SELECT COUNT(accusedid)
FROM accused
```
Without distinction, there are 3219 people included in the accused table.

```{sql echo=TRUE, connection="witch_con"}
SELECT COUNT(DISTINCT accusedid)
FROM accused
```
With distinction, there are 3006 people included in the accused table.

d) Display the columns firstname, sex, and age for 5 cases in the accused table.
```{sql echo=TRUE, connection="witch_con"}
SELECT firstname, sex, age
FROM   accused 
WHERE age > 50
LIMIT 5
```

e) Count the number of nonmissing values for age in the data.
```{sql echo=TRUE, connection="witch_con"}
SELECT COUNT(age)
FROM accused
```
There are 166 nonmissing values for age in the data.

f) Show a list of unique occupations.
```{sql echo=TRUE, connection="witch_con"}
SELECT DISTINCT occupation
FROM accused
```

# 2. Seeing the Devil
a) List the unique devil_types in the data.

```{sql echo=TRUE, connection="witch_con"}
SELECT DISTINCT devil_type
FROM devilappearance
```

b) How many of the sightings mention the word "black" in the description? 
```{sql echo=TRUE, connection="witch_con"}
SELECT COUNT(devil_text)
FROM devilappearance
WHERE  devil_text LIKE '%black%'
```

There are 121 sightings mention the word "black" in the description.

c) What proportion of the devils (in devil_type) are male?
```{sql echo=TRUE, connection="witch_con"}
select devil_type, count(*) * 100.0 / (select count(*) from devilappearance) as percentage
from devilappearance
group by devil_type 
order by percentage desc
```

From the table, we can see that about 63.13% the devils (in devil_type) are male.

# 3. The trial

a) What are the average and maximum numbers of male and female accusers?

```{sql echo=TRUE, connection="witch_con"}
SELECT AVG(female_accusers), MAX(female_accusers), AVG(male_accusers), MAX(male_accusers)
FROM   trial 
```
From the table, we can see that:
The average number of female accusers is 0.2599;
The maximum number of female accusers is 27;
The average number of male accusers is 0.4182;
The maximum number of male accusers is 48.

b) Count the number of sentences by sentence type. List them in a table (in descending order), excluding missing values. Rename the column headings to something sensible.
```{sql echo=TRUE, connection="witch_con"}
SELECT sentence as "sentence type", COUNT(sentence) as number
FROM   trial 
WHERE sentence <> "NA"
GROUP BY sentence
ORDER BY number desc
```
c) Do the number of accusers matter for the verdict? Compare the average number of accusers by the type of verdict. Again make sure the table is sorted and the headings make sense.

```{sql echo=TRUE, connection="witch_con"}
SELECT verdict as "verdict type", avg(female_accusers + male_accusers) as "average number of accusers"
FROM   trial 
WHERE verdict <> "NA"
GROUP BY verdict
ORDER BY "average number of accusers" desc
```

4. Tortured Truth (Bonus)
a) Left join the trial and confession tables. For what share of trials does the database record confessions? Create a results table with the number of all trials, the number of confessions, and the share of trials with confessions recorded.

```{sql echo=TRUE, connection="witch_con"}
SELECT 
COUNT(confession.confessionid) AS "number of confession",
COUNT(trial.trialid) AS "number of trial",
ROUND(COUNT(confession.confessionid)/COUNT(trial.trialid) * 100, 2) AS "share of confession"
From trial
LEFT JOIN confession
ON confession.trialref = trial.trialref 
```

From the table, we can see that 27.71% share of trials record confessions.


b) Only a small number of trials have records of torture. Is there a higher share of confessions among trials with records of torture than trials without such record?

```{sql echo=TRUE, connection="witch_con"}
SELECT 
COUNT(confession.confessionid) AS "number of confession",
COUNT(trial.trialid) AS "number of trial",
ROUND(COUNT(confession.confessionid)/COUNT(trial.trialid) * 100, 2) AS "share of confession"
From trial
LEFT JOIN confession ON confession.trialref = trial.trialref
LEFT JOIN torture ON confession.trialref = torture.trialref
WHERE tortureid is not null
```


```{sql echo=TRUE, connection="witch_con"}
SELECT 
COUNT(confession.confessionid) AS "number of confession",
COUNT(trial.trialid) AS "number of trial",
ROUND(COUNT(confession.confessionid)/COUNT(trial.trialid) * 100, 2) AS "share of confession"
From trial
LEFT JOIN confession ON confession.trialref = trial.trialref
LEFT JOIN torture ON confession.trialref = torture.trialref
WHERE tortureid is null
```

Yes, there is a higher share of confessions among trials with records of torture than trials without such record.
With records of torture, the share is 100%, while without such record, the share is 26.96%.
